### 2021-02-15 include/lampiran.tex
lampiran

>>>>

\section{Data Hasil Percobaan Waktu Komputasi dan FPS}

\subsection{Average Blur}
\csvautolongtable{tables/performance-fps-time/aveblur.csv}

\subsection{Gaussian Blur}
\csvautolongtable{tables/performance-fps-time/gaussblur.csv}

\subsection{Laplacian}
\csvautolongtable{tables/performance-fps-time/laplacian.csv}

\subsection{Sharpening}
\csvautolongtable{tables/performance-fps-time/sharpen.csv}

\subsection{Sobel Horizontal}
\csvautolongtable{tables/performance-fps-time/sobelhor.csv}

\subsection{Sobel Vertical}
\csvautolongtable{tables/performance-fps-time/sobelver.csv}
